Response to referee

### 2024-04-17 paper/resp_referee.qmd
improvement

> 4. Page 7, line 40: why say the series is extended by one year? The extensions are for as many 
> years as needed by the particular filters (typically, half their length in years).

@@

@@

> 9. Page 15, line 40: I couldn't find the matrix $T$ defined. How is it connected to timeliness? 
> That is, when you display the entries of the matrix T, you need to make a connection between 
> those values and the concept of timeliness.

> 10. Page 15, line 53: I don't see why $v$ in this equation should be defined through the case bracket; 
> everything starting with "with" could be moved to the following text.

@@

@@

> 1. The authors should provide a clear definition of trend-cycle, $TC_t$, 
> and irregular, $I_t$. In other words, how is the decomposition 
> $y_t =TC_t+I_t$ identified? In section 1 they seem to hint at the interpretation 
> of $TC_t$ as the low-pass component of yt with cutoff frequency 
> $\pi/6$ (and correspondingly they interpret $I_t$ as the high-pass component). 
> This point should be clarified, I think. 
> Related questions are: are $y_t$ and its components stochastic or deterministic? 
> The treatment in section 1.2.1 suggests that $TC_t$ is 
> an unknown possibly nonlinear deterministic function of time. 
> The variance inflation factor $\sum_k \theta_k^2$ implies that $I_t$ is white noise.

> 2. The idea of minimizing the noise component ($M_\theta(I_t)\simeq 0$) is not
> very formal. Do you mean that the unconditional variance is minimized?
> Or the long run variance?

@@

> 4. The notation should be unified: why not writing $TC_t = \mu(t)$ and
> in section 2 using $t$ instead of $x$? The observation index i hould
> be replaced by $t$, as in section 2.1. Similarly, why not using ϵt
> directly and start section 1.2 by stating that you assume that yt is
> generated as $y_t = \mu(t) + \varepsilon_t$, etc.
> Secondly, you should clarify the meaning of (3), where you set
> $\mu(t) = u'_t\gamma + z'_t\delta$ (also you assume that the noise component has possibly a non-scalar covariance matrix, do you need the matrix $D$ for later treatment?

@@

@@

> - Page 4. The definition of the high-pass component (oscillations
in the frequency range from $\pi/6$ to $\pi$ as undesirable oscillations is
controversial.

> - Figure 1. In the caption, the ration $I/C$ was never defined before.
The description of the three panels should be better explained in
the main text.

@@

@@

@@

@@

@@

@@

>>>>

*This sections was simplified*

> 4. Page 7, line 40: why say the series is extended by one year? 
> The extensions are for as many years as needed by the particular filters (typically, half their length in years).

@@

The $\forall q$ was omitted and this section was rewritten to make it clearer.

@@

> 9. Page 15, line 40: I couldn't find the matrix $T$ defined. How is it connected to timeliness? 
> That is, when you display the entries of the matrix $T$, you need to make a connection between 
> those values and the concept of timeliness.

*More details are added to this section to explain how the matrix $T$ is defined by Grun-Rehomme et al. (2018).*

> 10. Page 15, line 53: I don't see why $v$ in this equation should be defined through the case bracket;
>everything starting with "with" could be moved to the following text.

*Indeed, the formula are corrected*

@@

*All the code will be in a github repository*

@@

> 1. The authors should provide a clear definition of trend-cycle, $TC_t$, and irregular, $I_t$. In other words, how is the decomposition $y_t =TC_t+I_t$ identified?
> In section 1 they seem to hint at the interpretation of $TC_t$ as the low-pass component of yt with cutoff frequency $\pi/6$ (and correspondingly they interpret $I_t$ as the high-pass component). 
> This point should be clarified, I think. 
> Related questions are: are $y_t$ and its components stochastic or deterministic? 
> The treatment in section 1.2.1 suggests that $TC_t$ is an unknown possibly nonlinear deterministic function of time. 
> The variance inflation factor $\sum_k \theta_k^2$ implies that $I_t$ is white noise.

> 2. The idea of minimizing the noise component ($M_\theta(I_t)\simeq 0$) is not very formal. 
> Do you mean that the unconditional variance is minimized?
> Or the long run variance?

@@

> 4. The notation should be unified: why not writing $TC_t = \mu(t)$ and in section 2 using $t$ instead of $x$? 
The observation index $i$ should be replaced by $t$, as in section 2.1. 
Similarly, why not using $\varepsilon_t$ directly and start section 1.2 by stating that you assume that $y_t$ is generated as $y_t = \mu(t) + \varepsilon_t$, etc.
Secondly, you should clarify the meaning of (3), where you set
$\mu(t) = u'_t\gamma + z'_t\delta$ (also you assume that the noise component has possibly a non-scalar covariance matrix, do you need the matrix $D$ for later treatment?)

@@

*More details on the definition $\varphi$ and $\rho$ was added using the real part ($\sum_{k=-p}^{+f}\theta_k\cos(\omega k)$) and the imaginary part ($\sum_{k=-p}^{+f}\theta_k\sin(\omega k)$) of the transfer function*

@@

*The $p$ for the period was replaced by $s$*

> - Page 4. The definition of the high-pass component (oscillations in the frequency range from $\pi/6$ to $\pi$) as undesirable oscillations is controversial.

> - Figure 1. In the caption, the ratio $I/C$ was never defined before.
The description of the three panels should be better explained in the main text.

@@

*Fixed*

@@

*More details are added to this section. The definition is more general than the polynomial ind*

@@

Other (non-exhaustive) [only remarks that require a response]
- P2 L8:  “X-13ARIMA seasonal adjustment method” -- The software is officially X-13ARIMA-SEATS, but the seasonal adjustment method itself is X-11 (applies to subsequent occurrences as well)

- P2 L29:  “good properties” -- This could be less vague.

- P7 L58:  There is a $q$ introduced here via “$w_t^q$ for $t>q$” that shows up later as well, but  itself does not appear to be properly defined otherwise.

- P9:  Author lists a number of quality criteria in Table 1.  It may be obvious for some of these, but it would be helpful to the reader to indicate whether lower values or higher values are preferable for each, either in the table or in the accompanying exposition.

- P11 L22:  “$2h+1 \geq d+1$” -- Why not just say $2h\geq d$?

This sentence was rephrased: $d+1$ refers to the number of parameters to estimate and $2h+1$ the number of observations.

- P14 L33:  More exposition wrt Table 2 may be helpful, as there is a fair amount of information to digest.

*Table 2 was removed*

- P14 L45:  What is the rationale for this combined measure $EQM_w=A_w + S_w + T_w + R_w$?  Looking at the expressions for these four from Table 1, it is apparent that $A_w$ and $T_w$ sum up (the two have the same integrand, and the resulting sum is the integral from 0 to $\pi$), and same goes for $S_w$ and $R_w$.  
And it should probably be explicitly stated what $EQM_w$ stands for prior to introducing it in the table.

*This table was removed but to answer your question the criteria comes from the decomposition of the mean squared error into four quantities*

- P19 L15:  “January 1960 and December 2020” -- As noted previously, is it worth considering an additional scenario with (simulated) series of shorter length?

@@

This section was rewrite to make it clearer.

@@

This symbol was referring to integer interval, it was removed to avoid confusion (for example $[[1,d]]$ was replaced by $\{1,2,\dots, d\}$).

@@

More explanations was added to this paragraph: the formula comes from local regression theory simplified because we are here in the case of local polynomial approximation.
